---
title: "Visualization samples"
output: github_document
---

``` {r ref, echo=FALSE, message=FALSE, warning=FALSE}
library(choroplethr)
library(choroplethrMaps)
library(gridExtra) # to control the output structure
```

## Choropleth maps

Below are some examples of a simple choropleth map using choroplethR from Ari Lamstein, which is a terrific package.

First, here is the population for a select number of southern states using the ACS data set and the most recent 5 year file.
```{r pop, echo=FALSE, message=FALSE, warning=FALSE}
county_choropleth_acs(tableId="B01003", endyear = 2011, span = 5, num_colors = 1, state_zoom = c("tennessee", "georgia", "alabama", "mississippi"))
```

And then, using the same data source, here is a snapshot of income for the same states.
```{r choro, echo=FALSE, message=FALSE, warning=FALSE}
income_region <- county_choropleth_acs("B19301", num_colors = 1, state_zoom = c("tennessee", "georgia", "alabama", "mississippi") )
income_tn <- county_choropleth_acs("B19301", num_colors = 1, state_zoom = "tennessee")

#grid.arrange(income_region, income_tn, ncol=2)
income_region
```

#### Examining distribution of race within Tennessee

(work in progress)

```{r chorogrid, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
df_white <- county_choropleth_acs("B02008", num_colors = 1, state_zoom = "tennessee")
df_black <- county_choropleth_acs("B02009", num_colors = 1, state_zoom = "tennessee")
#df_hisp <- county_choropleth_acs("B03002", num_colors = 1, state_zoom = "tennessee")

# TO DO:
# grid.arrange(df_white, df_black, df_hisp, ncol=3)

df_white

df_black

#df_hisp

```


## Leaflet maps (to come)



